
\section{Conclusion}
\label{s-con}
This paper serves as a comprehensive description of our solution for securely integrating document storage systems such as storage clouds and data centers with a blockchain network such that access to those storage systems is governed by policies regarding payments and access permissions specified in blockchain smart contracts. The solution positions a gateway system in between the storage and the blockchain network that enforces these policies regarding storage access. The gateway is designed to be easily replicable and tolerant to internal failures.

The solution's philosophy is that for the management of bulky and, in particular, static information such as documents and images, the blockchain technology should take the responsibility for access control, payment processing, document integrity insurance, and auditing while a storage technology should hold the coveted information and provide access to them. This partitioning of responsibility provides the flexibility of using a mature storage technology in blockchain powered applications with added security and accountability that currently only the blockchain technology can offer. Our solution is quite different from the blockchain based storage alternatives that store bulky information directly within the blockchain network using complex mining incentive mechanism and still burdens the user with information availability and integrity insurance.             

There are three aspects of our solution: first, cryptographically secure and accountable protocols for handling information upload and download with the external storage; second, a generic access permission control strategy for launching those protocols; finally, a mechanism to deal with reversal of blockchain transactions related to the protocols and access control. The paper described all three of them. There are significant room for improvement in all three aspects, in particular, for performance betterment. That will be a target of future research.         
 
