\section{Document Upload and Download Protocols}
\label{s-updown}
For the discussion of this section, we assume that both document upload and download with the external storage involves blockchain payments. Both protocols heavily use symmetric key cryptography in various steps for information and payment security. We refer the reader to \cite{1455525} for an introduction to cryptography and to \cite{Daemen99aesproposal:} for AES symmetric key cryptography in particular.

\subsection{Quality Criteria for Upload/Download Protocol Design}
We decide on a set of behavioral characteristics for the document upload and download protocols. These characteristics are classified into two groups based on the expectation of the storage integration gateway and that of the user from the protocols. 
From the gateway's perspective the following characteristics are important:
\begin{itemize}
\item Accountability: all actions are traceable in the blockchain.
\item Independence from storage system failure: payment is collected only after all interactions with the storage system are done successfully.
\item Guaranteed Payment: the user can neither fool it to do unnecessary work nor withheld the payment after the work is complete.
\item Fault-tolerance: all local state information should be derivable from the blockchain ledger so that the gateway can restart easily after a failure or data corruption.  
\item Security from Malicious Miners: no mining nodes can snatch the payment intended for the gateway. 
\end{itemize}   
From the user's perspective, on the other hand, the following characteristics are desired from the protocols:
\begin{itemize}
\item Security: no one else can interrupt the storage session intended for the user. 
\item Payment Security: the user must be able to get refunds if he/she does not get the proper service. 
\item Confidentiality: the underlying document cannot be retrieved by others (users or miners) using the audit trail of the protocol execution in the blockchain ledger.
\end{itemize} 
Propriety of both groups of behavioral characteristics is self-evident. Hence we do not elaborate on them further. During the protocol description, we discuss how different aspects of the protocols serve to achieve the mentioned characteristics. 

\subsection{Document Upload Protocol Description}
The document upload protocol is composed of three main phases:
\begin{enumerate}
\item Token deposition by the {\it user}.
\item Document upload processing by the {\it gateway}.
\item Then, payment finalization by the {\it user}.
\end{enumerate}
Each phase of the protocol involves multiple interaction steps among various system components. Figure~\ref{fig:up-proto} presents the sequence diagram of the protocol.
\tikzset{every picture/.append style={transform shape,scale=.60}}
\begin{figure}
  \begin{sequencediagram}
    \newthread{usr}{\it User}{}
    \newinst[1.1]{ac}{ \it Gateway}{}
    \newinst[1.1]{bc}{\it Blockchain Network}{}
    \newinst[1.1]{es}{\it Storage System}{}

    \begin{callself}{usr}{\it Generate Document Key $D_k$}{}
    \end{callself}
    \begin{call}{usr}{\hspace{0.5cm} \it Get Initial Token}{ac}{\it M}
        \begin{callself}{ac}{\it Generate token M with generated key $K_1$}{}
        \end{callself}
    \end{call}
    \begin{callself}{usr}{\it Generate $K_2$ and prepare N}{}
    \end{callself}
    \begin{call}{usr}{\hspace{1cm} \it Upload Document Info and Lock Fee}{bc}{}
    \end{call}
    \begin{call}{usr}{\hspace{0.8cm} \it Upload Document}{ac}{}
        \begin{call}{ac}{\hspace{2.5cm} \it Verify doc size, fee and token M}{bc}{}
        \end{call}
        \begin{call}{ac}{\it Upload document}{es}{\it location Information}
        \end{call}
        \begin{call}{ac}{\hspace{2.5cm} \it Store encrypted location information}{bc}{}
        \end{call}
    \end{call}
    \begin{call}{usr}{\hspace{1.5cm} \it Check upload Status}{bc}{}
    \end{call}
    \begin{call}{usr}{\it Unlock payment with $K_2$}{bc}{}
        \begin{call}{bc}{\it Decrypt $N$ with $K_2$, match with M}{bc}{}
        \end{call}
    \end{call}

    \begin{call}{usr}{\hspace{0.5cm} \it Finalize upload}{ac}{}
        \begin{call}{ac}{\hspace{1.5cm} \it Check payment status}{bc}{}
        \end{call}
        \begin{call}{ac}{\hspace{1.5cm} \it Withdraw fee with $K_1$}{bc}{}
        \begin{callself}{bc}{\it Decrypt $M$ with $K_1$, match caller}{}
        \end{callself}
        \end{call}
    \end{call}
  \end{sequencediagram}
\caption{Sequence diagram of the document upload protocol}\label{fig:up-proto}
\end{figure}
We now describe these steps as parts of the three protocol phases.

\subsubsection{Token Deposition}
The {\it user} generates a document key $D_k$ by performing a hash operation on some document information (document name $D_n$, document uploader blockchain address $DU_{addr}$ and document bearer contract address $DC_{addr}$) to identify the document.
The {\it user} requests the {\it gateway} to generate a token for uploading a document with document size $D_{s}$, document hash $D_{h}$, signature of document hash $DH_{sig}$, $DU_{addr}$ and $D_{k}$. The {\it gateway} validates the input data from the {\it user}. The {\it gateway} generates an AES symmetric key $K_{1}$ and encrypts its blockchain address $G_{addr}$ with the generated key and produces an payment token $M$.
\begin{equation}
\label{eq-u-1}
M = Enc (G_{addr}, K_1)
\end{equation}
The {\it gateway} calculates the document upload fee according to the payment strategy and returns the generated token $M$ and calculated upload fee to the {\it user}.

The {\it user} generates another secret key $K_2$, encrypts the payment token $M$ with $K_2$ to produce an upload token $N$.
\begin{equation}
\label{eq-u-2}
N = Enc (M, K_2)
\end{equation}
The {\it user} performs a transaction to the blockchain with token $M$ and $N$ and other document meta-data. During this operation, the calculated upload fee is also deposited to the blockchain smart contract from the user account.
 
\subsubsection{Document Upload Processing}
After the earlier transaction is mined, the \textit{user} sends the document upload request to the {\it gateway} with the actual document and its meta-data. The {\it gateway} verifies the input data and retrieves the payment token $M$ from the blockchain and verifies that it contains the {\it gateway's} address $G_{addr}$ by performing a decryption on token $M$ with key $K_1$. If all verifications succeed, the {\it gateway} uploads the document to the storage system\footnote{If the storage system allows gateway defined transferable upload sessions for users then the user can do the document upload instead of the gateway.} and stores an encrypted version of the location information in the blockchain. The {\it user} can verify that the document  upload is successful by checking the blockchain.

\subsubsection{Payment Finalization}
After a satisfactory verification of the outcome of upload, the {\it user} issues an unlock payment transaction with the \textit{user's} secret key $K_2$ to the blockchain. The smart contract unlocks the payment if the decryption result of $N$ with provided $K_2$ matches with stored payment token $M$.
\begin{equation}
\label{eq-u-3}
M = Dec (N, K_2)
\end{equation}
The user requests the {\it gateway} to finalize the upload. The {\it gateway} verifies the payment unlock status from the blockchain and issues a transaction to collect the upload payment with its secret key $K_1$. The smart contract decrypts payment token $M$ with $K_1$ and matches the result with the caller address $C_{addr}$. If the address matches with decrypted result, smart contract enables the payment to the caller address.
\begin{equation}
\label{eq-u-4}
C_{addr} = Dec (M, K_1)
\end{equation}

\subsubsection*{Protocol Analysis}
Since it is cryptographically hard to produce an alternative address and key pair that satisfies Equation \ref{eq-u-4}, only the {\it gateway} can collect the payment. On the other hand, since payment is locked until someone supplies proper $K_2$ in the transaction evaluating Equation \ref{eq-u-3}, which is only known to the {\it user}, the {\it user} ensures that the gateway cannot collect the payment until the {\it user} verifies that the document is successfully uploaded. In addition, since the document's location information in the external storage is recorded by the {\it gateway} in the blockchain in an encrypted form, none but the {\it gateway} can interpret this information for future reference. This simultaneously ensures information security and gateway fault-tolerance. Finally, that \textit{user} can issue the required transactions into the designated smart contracts indirectly ensures user authentication.

Note that we did not address the possibility that the upload protocol terminates halfway in the execution for some machine or network failure. This issue can be tackled easily by associating an expiry time with the payment locking transaction. If the protocol fails before the {\it gateway} uploads the document in the external storage system, the user can withdraw the payment after the expiry time. If the failure happens after the document upload in the external storage, then the {\it gateway} can never collect the payment as the user is no longer there to unlock the payment for it. Hence, the {\it gateway} simply removes the document from the external storage in such cases.      

\subsection{Document Download Protocol Description}
The document download protocol being illustrated in Figure~\ref{fig:down-proto} consists of four phases.
\tikzset{every picture/.append style={transform shape,scale=1}}
\begin{figure}
  \label{seq:downloadProtocol}
   \begin{sequencediagram}
    \newthread{usr}{\it User}{}
    \newinst[1.2]{ac}{\it Gateway}{}
    \newinst[1.2]{bc}{\it Blockchain Network}{}
    \newinst[1.2]{es}{\it Storage System}{}

    \begin{call}{usr}{\hspace{0.5cm} \it Get payment token}{ac}{\it  $T_p$, fee amount}
        \begin{callself}{ac}{\it Prepare $T_p$ with generated key $K_{a}$}{}
        \end{callself}
    \end{call}
    
    \begin{callself}{usr}{\it Generate $K_c$, $K_u$ and prepare $T_u$}{}
    \end{callself}
    \begin{call}{usr}{\it Deposit and lock fee}{bc}{}
    \end{call}
    
    \begin{call}{usr}{\hspace{0.5cm} \it Prepare session}{ac}{\hspace{0.1cm} \it $ENC_s$}
        \begin{call}{ac}{\hspace{1.5cm}\it Verify sign and payment}{bc}{\it $T_p$}
        \end{call}
        \begin{callself}{ac}{\it Verify $T_p$}{}
        \end{callself}
        \begin{call}{ac}{\it Generate session}{es}{$S$}
        \end{call}
        \begin{callself}{ac}{\it Generate $K_s$ and prepare $ENC_s$} {}
        \end{callself}
        \begin{callself}{ac}{\it Prepare Hash $H_s$ of $ENC_s$}{}
        \end{callself}
        \begin{call}{ac}{\hspace{0.3cm}\it $H_s$}{bc}{}
        \end{call}
    \end{call}

    \begin{call}{usr}{\hspace{1.0cm} \it verify $H_s$ is the hash of $ENC_s$}{bc}{}
    \end{call}
    \begin{call}{usr}{\hspace{1.0cm} \it Unlock payment with $K_u$, $D_k$, $U_{addr}$}{bc}{}
    \end{call}
    
    \begin{call}{usr}{\it Get session}{ac}{}
        \begin{call}{ac}{\hspace{3.0cm} \it Verify signature and payment status}{bc}{}
        \end{call}
        \begin{call}{ac}{\hspace{3.2cm} \it Withdraw payment with $K_a$, $ENC_{ks}$}{bc}{}
        \end{call}
    \end{call}

    \begin{call}{usr}{\hspace{0.8cm} \it Get encrypted session encryption key }{bc}{$ENC_{ks}$}
    \end{call}
    \begin{call}{usr}{\it Dec($ENC_s$, Dec($ENC_{ks}$, $K_c$))}{usr}{\it $S$}
    \end{call}
    \begin{call}{usr}{\it Download document}{es}{\it Document}
    \end{call}
  \end{sequencediagram}
\caption{Sequence diagram of the document download protocol}\label{fig:down-proto}
\end{figure}
\begin{enumerate}
\item Token deposition by the {\it user}.
\item Download session creation by the {\it gateway}.
\item Payment approval by the {\it user}.
\item Finally, document download by the {\it user}.
\end{enumerate}
The phases are described in more detail below. 

\subsubsection{Token Deposition}
The {\it user} requests the {\it gateway} to generate a document download payment token with the document key $D_k$, document hash $D_{h}$, {\it user's} blockchain address $U_{addr}$, and signature of document hash $DH_{sig}$. The {\it gateway} verifies the input data, generates a payment secret key $K_a$ and encrypts its blockchain address $G_{addr}$ with the secret key and produces a payment token $T_{p}$. 
\begin{equation}
\label{eq-d-1}
T_p = Enc (G_{addr}, K_a)
\end{equation}
The {\it gateway} also calculates the fee according to the payment strategy to download the document and returns the payment token $T_p$ with the calculated download fee to the {\it user}.
After receiving the payment token, the {\it user} generates two symmetric keys $K_c$ and $K_u$. $K_c$ is the common conversation secret shared only with the {\it gateway}. The {\it user} generates an payment unlock token $T_u$ by encrypting $T_p$ with the key $K_u$.
\begin{equation}
\label{eq-d-2}
T_u = Enc (T_p, K_u)
\end{equation}
The {\it user} then issues a download payment transaction to the blockchain with two tokens $T_p$ and $T_u$, and some document related information that deposits the download fee in the blockchain smart contract.

\subsubsection{Download Session Creation}
After the download payment transaction is mined, the {\it user} issues a prepare download session request to the {\it gateway}. During this request, the {\it user} sends document bearer contract address $DC_{addr}$, signed document key $DK_{sig}$, $U_{addr}$, $D_k$, $D_{h}$, and $K_c$. The {\it gateway} validates the input data, retrieves the payment token $T_p$ from the blockchain and verifies by decrypting it with $K_a$ and matching the result with its own blockchain address $G_{addr}$. 
\begin{equation}
\label{eq-d-3}
G_{addr} = Dec (T_p, K_a)
\end{equation}
After successful address verification, the {\it gateway} retrieves the external storage information for the document and requests the {\it storage system} for a session $S$ to download the document. The {\it gateway} then generates a secret key $K_s$,  encrypts $S$ with $K_s$ and produces an encrypted session $ENC_s$. It also encrypts the document key with the common secret $K_c$ and produces an encrypted document key $ENC_{dk}$. 
\begin{equation}
\label{eq-d-4} 
ENC_s = Enc (S, K_s)
\end{equation}
\begin{equation}
\label{eq-d-5} 
ENC_{dk} = Enc (D_k, K_c)
\end{equation}
The {\it gateway} then prepares a hash, $H_s$, of $ENC_s$ and issues a transaction to the blockchain with $H_s$ and $ENC_{dk}$. The {\it gateway} locally stores all input data and returns $ENC_s$ to the {\it user}.

\subsubsection{Payment Approval}
The {\it user} verifies that the hash of $ENC_s$ is stored in the blockchain by the {\it gateway} then issues a transaction to unlock the payment with $K_u$, $D_k$ and $U_{addr}$. The smart contract unlocks the payment by decrypting the unlock token $T_u$ with the secret key $K_u$ provided by the {\it user} and matching the result with the payment token $T_p$. 
\begin{equation}
\label{eq-d-6} 
T_p = Dec (T_u, K_u)
\end{equation}
The {\it user} then issues a request to the {\it gateway} to get the download session encryption key with $D_k$, $DK_{sig}$ and $U_{addr}$. The {\it gateway} verifies the input data and encrypts the session secret $K_s$ with common conversation secret $K_c$ and produces an encrypted session encryption key $ENC_{ks}$.
\begin{equation}
\label{eq-d-7} 
ENC_{ks} = Enc (K_s, K_c)
\end{equation}
The {\it gateway} issues a blockchain transaction to withdraw the payment with the $K_a$ and $ENC_{ks}$. The blockchain smart contract enables the download payment fee to the caller address if the decrypting result of payment token $T_p$ with $K_a$ matches with the caller address. It also stores $ENC_{ks}$ with the download document information in blockchain.

\subsubsection{Document Download}
The {\it user} then collects the encrypted session encryption key $ENC_{ks}$ from the blockchain. The {\it user} first decrypts the encrypted session encryption key $ENC_{ks}$ with the common secret $K_c$ and retrieves the session secret key $K_s$, then decrypts the encrypted session $ENC_s$ with $K_s$ to retrieve the original session $S$.
\begin{equation}
\label{eq-d-8} 
K_s = Dec (Enc_{ks}, K_c)
\end{equation}
\begin{equation}
\label{eq-d-9} 
S = Dec (Enc_s, K_s)
\end{equation}
Finally, the {\it user} downloads the document directly from the storage system using the session $S$.

\subsubsection*{Protocol Analysis}
Payment security for both the {\it user} and the {\it gateway} is ensured as it was in the upload protocol using a pair of encrypted tokens and proper sequencing of the payment related blockchain transactions. Likewise, all steps of the download protocol are also reflected on the blockchain smart contract. This ensures gateway accountability. Further, the {\it gateway} again collects the payment only after completing its interaction with the {\it storage system} to protect itself from any blame related to latter's failure. Finally, information related to the storage session  is recorded in the blockchain in encrypted form while the key $K_c$ for decrypting it is shared securely between the {\it user} and the {\it gateway}. Hence none but these two entities can use the session to get access to the document.

One aspect of the download protocol requires particular attention. This is related to unlocking of the download fee by the {\it user} before he/she can verify that the storage session related information supplied by the {\it gateway} is accurate. Since the {\it user} can be malicious, payment must be unlocked for the {\it gateway} before the {\it user} can decrypt the external storage session related information. However, this ordering opens the possibility that the {\it user} ends up paying for an invalid storage session or dispute its validity when it is actually valid. Therefore, a mechanism is required for automatically resolve any dispute related to external storage session in the blockchain smart contract. This is facilitated by the series of encryption related to the conversation secret $K_c$ and the storage session $S$.

To submit a claim about an invalid session, the {\it user} sends $K_c$ and $ENC_s$ in the blockchain smart contract. That the user has supplied the valid conversation secret is verified by performing the inverse of Equation \ref{eq-d-5} and matching the answer with the document key $D_k$. Since it is the {\it gateway} who did the original transaction, the {\it user} also establishes that the provided $K_c$ value was known to the {\it gateway}. Now the blockchain smart contract itself can compute Equation \ref{eq-d-8} and \ref{eq-d-9} to retrieve the session $S$. It then computes a hash of $S$ and checks if that matches $H_s$ which being stored in the blockchain by the {\it gateway}. If both hashes matches then the {\it user's} session invalidity claim is serious. Then the {\it gateway} maliciousness and external storage  malfunctioning should be investigated. Otherwise, the {\it user's} claim is ignored.          

